\texttt{davos}: The Python package smuggler

### 2022-09-19 paper/main.tex
whitespace-only changes (pycharm removed trailing whitespace)
updates to paragraphs 1 & 2

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern scientific research often entails writing software code for a wide variety of purposes throughout the scientific process:
researchers across disciplines design and implement experimental paradigms; collect, process, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
However, one requirement common to nearly all research-related code is that it behave consistently and predictably every time it is run, both over time and across different users.
This stability can be crucial to ensuring, for example, that data are collected under the same conditions (e.g., across recordings, trials, or subjects) over multiple months or years, and can be processed and analyzed consistently by collaborators across multiple institutions or countries.
Additionally, modern open science practices encourage sharing research code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work.
Much of the benefit afforded by freely available research code relies on users ability to execute it and achieve the same result as its original author.

Python has become one of the most widely used and fastest-growing scientific programming languages by combining an accessible, high-level syntax with the availability of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}. 
The Python ecosystem offers an extensive data science toolkit, with platforms for interactive programming (e.g., Project Jupyter \cite{KluyEtal16}, Google Colaboratory), community-maintained libraries for data manipulation (e.g., NumPy \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}), frameworks for training complex machine learning models (e.g., scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging Face \cite{WolfEtal20}), and myriad other resources. 
However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same library may behave differently, adopting different syntax, adding or dropping support for specific functions or other libraries, addressing (or introducing) bugs, and so on. 
While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages. 
Ensuring Python code behaves consistently over time and across users therefore typically requires making sure it is always run with the same specific set of versions for each package used.

>>>>

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern scientific research often entails writing software code for a wide variety of purposes throughout the scientific process.
Researchers across disciplines may design and implement complex experiments; collect, store, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
However, one requirement common to virtually all forms of research-related code is that its behavior and outputs remain consistent and predictable, no matter when, where, or by whom it is run.
This stability can be crucial to ensuring, for example, that data are collected under the same conditions (e.g., across recordings, trials, or subjects)
%^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
over multiple months or years, and that they can be accessed, processed, and analyzed consistently by a research team that may be spread across multiple institutions or countries.
Additionally, modern open science practices encourage publicly sharing research code and data so that others may explore, reproduce, learn from, and build upon existing work.
Much of the benefit afforded by freely available research code depends on users' ability to execute it and achieve the same result as its original author.

Python \cite{vanR95} has become one of the most widely used and fastest-growing scientific programming languages, in part by combining an accessible, high-level syntax with a rich ecosystem of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}.
The Python ecosystem offers an extensive data science toolkit with platforms for interactive programming (e.g., Project Jupyter \cite{KluyEtal16}, Google Colaboratory), community-maintained libraries for data manipulation (e.g., NumPy \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}), frameworks for training complex machine learning models (e.g., scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging Face \cite{WolfEtal20}), and myriad other resources.
However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code:
different versions of the same library may behave differently, adopt changes in syntax, expose different functions and interfaces, add or drop support for specific hardware or software, write (or expect to read) files in different formats, fix (or introduce) bugs, and so on.
While these issues exist to some extent in any software language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
Ensuring Python code behaves consistently over time and across users therefore typically requires ensuring it is always run with the same specific set of versions for each third-party package used.
%Ensuring Python code behaves consistently over time and across users therefore typically requires guaranteeing that the same specific version of each required third-party package is used, every time it is run.
